\documentclass[../Main.tex]{subfiles}

\begin{document}

\section{Prototype 1}

The following document contains all the goals the first prototype of Steel Purge will reach at the end of the iteration. The goals will be very basic and must define the foundational structure of the game. Many of the current ideas written in the idea-document will be a part of the goals, so they will not be reiterated here.

\subsection{Gameplay}

The game is going to be a 2D action platformer in a tile-based world. The player is able to jump and walk like a normal platforming video game.

\subsubsection{Health}

The player has a total of 100 health. When the player takes damage, a timer will start which, when completed, starts a health regeneration process. The regeneration process is very slow and should only work out of combat. 

\subsubsection{Weapon mechanics}

Weapons can fire automatically by holding down a button or key. Weapons can shoot to the left, right or downwards. Firing downwards produces recoil which can propel the player upwards. Weapons can also be used to melee and they each have special damage numbers. They have special abilities which can be powered using unique fuels that can be crafted or found. 

\subsubsection{Movement mechanics}

The player will be able to slide on the ground to increase their speed shortly or to preserve their momentum if they managed to move fast initially. Using their weapon, the player can also aim downwards to fire which propels them a little higher each time they shoot. When the player walks for long enough, they will automatically start running slightly faster.

\subsubsection{Enemies}

 There will be two enemies and one boss at the end of the first level. When enemies are killed to hit, they drop scrap metal for the player. Enemies usually have a critical hit area on top of their head, meaning hits on this area will deal extra damage to them. 

\paragraph{}
The first enemy is the "XW Rush-Rogue", which is a small enemy with a high health pool. As soon as it sees the player, the enemy will rush towards the player. If the enemy hits the player, then it will explode dealing massive damage, almost killing the player. Since it has so much health and rushes towards the player, the enemy can receive massive critical hit damage that instantly kills it.

\paragraph{}
The second enemy is the "AR43 Executor". This enemy shoots three metal rods at a time and runs towards the player after each shooting interval. This enemy can also melee the player, which is why it runs towards them every interval.

\paragraph{}
The last enemy, which is a boss, is called the "TX9 Titan of Law". This enemy is a tall robot and has critical hit areas on its knees. It smashes the ground and causes an earthquake dealing damage to the player. There should be platforming areas for the player to be able to reach the critical hit areas with a high risk and high reward. 

\subsubsection{Scrap}

Scrap is a material/currency which can be used to create/buy weapons and fuel. 

\subsubsection{Pickable items}

Steel Purge will have several items the player can pick up. For this prototype, there will only be scrap and weapons that can be picked up. The fuels must be crafted from scrap only.

\subsubsection{Checkpoints and crafting stations}

The checkpoints on the level will also serve as crafting stations. The player can craft respective fuels for their weapon they can craft using the scrap they collected from enemies

\subsection{User interface}

\subsection{Art}

\subsection{Music}

\subsection{The first level}

\end{document}