\documentclass[../Main.tex]{subfiles}

\begin{document}

\section{Story}

% It is the year 2034 and the world is undergoing a global industrial revolution. This time, military technology is the hope of every land's survival. Countries are putting resources, including their people, into weapon production in order to dominate any war that inevitably arises. You are working for district Goliath-A1, the primary weapons factory of your government that spans two thirds of the capital. Every employee must wear a specialized industrial body armor which protects from any accidental friendly fire at the workplace. This factory only produces ballistic infantry weapons, but your curiosity doesn't fool you. Seeking around the deeper structures of the factory, you find a hatch which seemingly would lead to a sewer. Being your curious you, you open the hatch and for some reason strong chiming winds throw you into the hole which leads to a strangely large sewer. It is dark, but some lights work. Through the dark alleys of the sewer, strange metalized humanoid beings emerge with malicious intent. An industrial revolver that came along with the winds rests on the ground. Your options become clearer by the second.

\subsection{World elements}

\paragraph{Auxillite} 

\paragraph{Arm Cannon}

\subsection{The world's backstory}

For one hundred years humans managed to thrive across solar systems with their new found technology. Every stone planet became habitable using extractors that transferred energy inside planetary cores to artificial atmospheres. The human race was to never face extinction and could be seen to dominate the cosmos. Nevertheless, the homo sapiens alone did not have the physical strength, nor durability, to achieve the greater heights of cosmic habitation. The majority of their forces consisted of a robotic humanoid technology, known as the Auxillite. Varying shapes and sizes of these obedient robots fit almost every need one could imagine. From construction workers to home servants, there was not a need one Auxillite could not fulfil. With the help from all these robotic helpers, planet HS-921, or "Portus", became the central habitable planet for all the humans.

\paragraph{}
Mass production of various technologies and desirable living conditions rested at Portus with a shining bright future. The production was so vast that several other habitable exoplanets depended on this haven. Communication technologies were still at an early stage for the humans, so planetary intercommunication was not yet optimal and messages would take several years to reach anyone on the outskirts. Despite the limitations, remarkable Portusian scientists accounted for any crisis that would require a distress signal towards neighbouring planets.

\paragraph{}
There is a reason the thrive lasted for only a century. On one Portusian day, a strange and sudden impulse hit the planet, freezing all computer-based technology, including all the Auxillites. The freeze lasted for several days and put the people of Portus' lives at risk. New measures had to be developed to help survive independently from the robotic helpers until a solution to this mysterious demise came to be. Several decades passed without assistance from the Auxillites, nor even people of the exoplanets. The Auxillites on Portus were even more abundant than the human population. This fact posed a threat for the Portusian people, as the robots started to suddenly function again, but without control. A strange vicious aura emitted from every Auxillite and no one was able to command the robots, nor even hack their source code. They began capturing people from homes, workplaces and city centrals relentlessly. Anyone who opposed them were neutralized. Several military forces had to defend against the abundant attacks from the Auxillites. However, since the military technology was computer-based and forces largely consisted of Auxillites, it rendered everyone defenceless. 

\paragraph{}
The people of Portus were no longer thriving, but hope was never lost. A lonesome and mysterious inventor by the name of Dr. Hamilton discovered that the thunderstorms on planet Portus could generate a special type of energy. Referred to as "Tempest Currents", it is a resource able to disrupt and manipulate electronics to anyone's will.  This became a gateway to a more advance technology. Hamilton's work appeared to be Portus' greatest hope for prevail, as the scientist enabled hundreds of revolutionary technologies made to counter the Hostile Auxillites. Computer technology was based on this new energy and could never be hacked or interfered with. Decades upon decades of  technological development showed a miraculous advancements in the Portusian society. The people saw hope, but not with peace...

\paragraph{}
Hostile Auxillites still perished anyone who opposed their unknown malicious intent. This problem had to be dealt with. Military forces needed to change with the new technology simultaneously; this was not an easy feat. Soldiers needed weapons and equipment that could counter Hostile Auxillite forces without suffering instant fatal damages from any attack. Dr. Hamilton was ready to engage with this problem and quickly invented a solution. The Ferro Suit ended up as the final key to purge the Auxillian hordes. This suit possessed infinitesimal particles of Tempest Energy that could power the suit for several centuries. With this immensely efficient energy, the Ferro Suit was capable of protecting its user against large amounts of physical damage, but also serve as a spacesuit, among other things. The suit was not complete without a set of Arm Cannons: a pair of modular gauntlets capable of firing special projectiles and perform several other special actions. These gauntlets were also powered by the Exosuit's Tempest Energy, yet some actions cannot be performed without a required physical element. For instance, a pair of flamethrower Arm Cannons require gasoline to fire, and the Tempest Energy only amplifies its power and efficient consumption. The Ferro Suit was not without its flaws, as it was heavy and only trained specialists were capable of wearing it and mastering its performance. Despite the Exosuit having a mechanism to move on its own, the user still needed to train for years in order to master its movement. Nevertheless, the Ferro Suit became a great weapon and survival tool for its user. 

\paragraph{}
Dr. Hamilton did not implement the century-long lifespan of the Ferro Suit without reason. Despite its highly capable protective mechanisms, the user was still at fatal risk in battle, and these highly trained soldiers were not expendable, either. In secret, Hamilton created a high-power central processing unit able to store anyone's conciousness inside it. In the event that the user was facing fatal injuries, the suit would use the remaining time of the user to extract their mind into the system. This came at a price, as the user's brain would disintegrate. This technology was a secret last-ditch effort from Hamilton, as the mechanism did not store the user's memories and only preserved their skills as a fighter. Hamilton hoped this technology would never be put into use, but the inventive nature of this scientist did not stop them from creating it.

\subsection{Campaign story}




\end{document}