\documentclass[../Main.tex]{subfiles}

\begin{document}


\section{Weapons}

Every weapon is a pair of gauntlets that can shoot projectiles and used for melee. The weapons in Steel Purge will be the primary source of attacking enemies. Weapons have infinite ammo. The weapons also have some extra specialities spoken about in this chapter. The player should be able to carry one weapon at a time, but can switch to a different one when entering a menu.

\subsection{Weapons are unique}

Every weapon should signify a special trait or element that only a particular weapon can posses. This will affect what they shoot, what their entire kit is based on, a unique passive ability and a single special ability. 

\subsection{Weapon ordinance}

Weapons, in addition to firing, have a special ability called an \emph{ordinance}. It uses a specific resource in order to be utilized. This ability should usually allow for utility, mobility and lethality.

\subsection{Weapon mechanics}

Each weapon has a special mechanic to them that are used both for combat and level design. For instance, a flame weapon that can burn down ice barriers which hold access to secret areas. Most of the time, the unique mechanics of the weapon should be emphasized in a level in order to introduce its uniqueness. 

\subsection{All Weapon Ideas}

This section consists of all the ideas for each weapon.

\paragraph{H-28}

Standard issue arm cannons delivered by Hamilton Armory. Fires directed energy projectiles in a moderate fire rate. 

Ordinance: Laser Burst - Fire two powerful laser shots that do collateral damage, even through critical hitboxes.

Recoil Dash Projectile: A dual shotgun-pattern of energy projectiles.

Storm Core Power-Up:

\paragraph{Joule}

Shoots kinetic energy orbs. The orbs create an explosion on impact that deals damage and knocks enemies away. The explosion can also be used to propel the player.

Ordinance: Seismic Slam - Jump into the air and slam the ground to unleash a kinetic blast dealing damage to enemies. Enemies caught in the blast are impaled for a short moment. Slamming on top of enemies does critical damage. 

Recoil Dash Projectile: Large kinetic orb that absorbs any projectile that hits it

Mechanic: Explosive orbs can knock away objects in certain puzzles

Storm Core Power-Up: Force Storm - Use the kinetic forces in your weapons to blast enemies away. Enemies that hit a wall take significant damage from the impact. 

\paragraph{Firewall}

Flame-thrower-shotgun gloves. Fires projectile flares that, upon consecutive hits, burns enemies.

Ordinance: Dragon's Breath - Activate a strong stream of fire that melts enemies to death. It can also act as a jet-pack when firing downwards.

Recoil Dash Projectile: Larger shotgun-blast than standard fire

Mechanic: Can break down obstacles weak to fire

Storm Core Power-Up: Inferno Storm - You suit constantly emits combustion, burning all enemies that come in contact with you along with their attacks

\paragraph{Falcon}

Launches sharp kinetic energy blasts through the wind in quad-bursts.

Ordinance: Aerial Charge - Manipulate the wind to charge through the air and strike enemies with great damage. Hitting obstacles in this state will stop the flight. 

Recoil Dash Projectile: Large gust that damages enemies and pushes them back

Mechanic: Allows the player to reach areas they otherwise could not

Storm Core Power-Up: Blade Storm - Your Aerial Charge ability no longer requires Ordinance fuel and is more readily available. Additionally, you receive a projected wind-sword that deals high damage to enemies. 

\paragraph{Neostar}

Ionic metal manipulator. Fires a constant volley of metallic debris extracted from ions in the air using magnetic forces. Multiple consecutive hits will magnetize the target causing all your projectiles to follow the target.

Ordinance: Magnetic Shield - Hold up a constant force of magnetism that blocks incoming metallic objects or enemies that are close to the force. Release the button to send back all objects to deal damage to other enemies. 

Recoil Dash Projectile: Large chunk of metal that targets enemies

Mechanic: Firing at metal surfaces will magnetize it allowing you to walk on it and reach greater heights. 

Storm Core Power-Up: Lead Storm - You shoot significantly faster and all fire is locked on to enemies facing you. 

\paragraph{Nullshatter}

Reality-shattering gauntlets that send two astral punches to a target at a time to deal damage. The punches can go through enemies and obstacles, but stop briefly when hitting anything.

Ordinance: Tunnel Punch - Punch through the barrier between reality and the Null Dimension to avoid all damage. A brief speed-boost is gained at the start of this ability and enemies can still be damaged, despite being in a different dimension. The map remains the same, but some indicated obstacles can disappear.

Recoil Dash Projectile: Large astral fist that damages enemies and passes through objects instantly.

Mechanic: Melee kills can open a portal to the null dimension. 

Storm Core Power-Up: Rift Storm - Send a large astral fist that, when hitting a surface or enemy, opens a portal to the Null Dimension and sucks all enemies in, trapping them in the portal. 

\subsection{Enemy ideas}

\subsubsection{Minions}

\subsubsection{Bosses}

\paragraph{Death Hornet X-09}

Spider-like boss that moves on the ground in its first form. At 75\% health it will turn into its second form and start flying above the player. For its first form, it can melee the player and drop XW Rush-Rogue enemies on the player. It also has a critical hit-box on top of its head. When it reaches its second form, it will start flying left to right and drop XW Rush-Rogues from the air. The player can still shoot at the boss by aiming up, but the damage will be minimal. The key is to ram-slide into the Rogues in order to uppercut them into the boss to deal even more critical damage since they explode on the boss. Three Rogue hits is enough to kill it from this point, but when it is only one hit left to kill it, the boss will move faster. 

\end{document}
