\documentclass[../Main.tex]{subfiles}

\begin{document}

\section{Game Goal}

The goal of the game is to complete all the levels. In addition to that, it is possible to complete puzzles in several areas of a particular level. 

\subsection{Level Completion}

The player can traverse to the end of a level in order to reach the end and complete it. As part of the game design, the player should defeat enemies in order to gain stronger resources for defeating the bosses at the end of each level.

\subsubsection{Bosses}

Every level features a boss at the end. Bosses are supposed to be unique and can be an individual entity or simply a part of the environment. To accommodate for having more levels in the game, boss designs may be reused with differing elements.  

\subsection{Progression system}

Steel Purge will have multiple ways to progress other than completing levels.

\subsubsection{Weapon unlocks}

The player can pick up weapons from dead soldiers as they progress through the game. The player should be rewarded with all the necessary weapons early on in the game in order to progress based on further level designs. 

\subsubsection{Kills}

Killing all enemies on a level should reward the player with something significant at the end of a stage. 

\subsection{Items}

As part of making the player's character stronger, there are multiple items they can carry to help them on the journey.

\subsubsection{Scrap}

Damaging or defeating enemies results in \emph{Scrap} being spawned on the ground. The player can pick up \emph{Scrap} and store them in their backpack. 

\subsubsection{Storm Core}

A key item obtained later in the game. This becomes a part of the player's suit and needs to charge up with kills. A full charge allows the player to activate a storm striking you with immense Tempest Energy. Your equipped weapon will signify a respective Storm Guardian that you will transform into. There are as many Storm Guardians as weapons in the game. 

Storm Guardians are deities formed by the Tempest Energy from Portus and they have unique powers.

\subsubsection{Ordinance Fuel}

The primary resource for activating the weapon mods. There are different types of fuels that at least two weapons will support. They can all be created from scrap or obtained by defeating specific enemies or picking them up by finding them in secret areas. Here are all the fuel ideas:

\paragraph{Napalm Cans:} Used to power pyrokinetic engines

\paragraph{EM Cells:} Electro-magnetic charge units used in directed-energy tools

\paragraph{Anti-matter} Capsules with safely contained anti-matter

\end{document}