\documentclass[../Main.tex]{subfiles}

\begin{document}

\section{Levels}

The levels in Steel Purge have unique platforming layouts and ways to be completed.

\subsection{Puzzles}

The player can enter areas that puts them into stasis and travel back in time to solve puzzles. In the story, the player's recollection of memories can transcend time. Solving the puzzles in each level will alter the present timeline which should help the main character achieve their goals in the story. I have yet to come up with something to facilitate this idea. 

\subsection{Shops}

The checkpoints on each level is a shop where the player can buy weapons and XE-Slugs using scrap.

\subsection{Sections/Areas}

Levels are divided into sections and the camera does not move further than the section. When the player moves out of the section the camera pans over to the next section. This mechanic does not apply to Purge Mode.

\subsection{Purge Mode}

Upon clearing a level the player is given the ability to enter Purge Mode on that particular level. This mode is essentially an event that occurs every now and again on cleared levels. The story aspect of this is that the Auxillites have suddenly appeared in one particular part of the world and you need to destroy them all.

Purge Mode is a round-based mode where you survive as many waves of enemies as possible. Every X rounds a mini-boss appears. This mode is designed to let the player farm more scrap if they have to.

\subsection{No-gravity areas}

Some levels have areas that do not include gravity. The player must use their weapons to gain momentum or step on gravity-inducing platforms. The Neostar weapon can also help create gravity by shooting at metallic obstacles. 

\subsection{Worlds}

Worlds are different thematic collections of levels. Here are some of the ideas for them.

\subsubsection{Antarctic ice-bunker}

\end{document}